---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fastr

<!-- badges: start -->
<!--
[![R-CMD-check](https://github.com/meixichen/fastr/workflows/R-CMD-check/badge.svg)](https://github.com/meixichen/fastr/actions)
-->
<!-- badges: end -->

*Meixi Chen, Martin Lysy*

---

## Description

The ***fastr*** (**F**actor **A**nalysis of **S**pike **T**rains in **R**) package 
provides methods for analyzing neural spike trains simultaneously recorded from multiple neurons,
with a focus on exploring the correlation between neurons. 

## Installation

Before installing ***fastr***, make sure you have ***TMB*** installed following the instructions [here](https://github.com/kaskr/adcomp/wiki/Download). 

To download the development version of this package, run 
```{r, eval=FALSE}
devtools::install_github("meixichen/fastr")
```

## Factor analysis of multi-neuron spike trains

The main method in this package models the multi-neuron spike trains within a factor analysis 
framework. Simply put, it assumes that the unobserved neural dynamics $\boldsymbol{x}(t)\in\mathbb{R}^q$,
which determines the observed spike trains $\boldsymbol{y}(t)\in\mathbb{R}^q$, can be written as
$\boldsymbol{x}(t)=\boldsymbol{\Lambda}\boldsymbol{f}(t) + \boldsymbol{\epsilon}(t)$,
where $\boldsymbol{f}(t)\in\mathbb{R}^d, \ d\ll q$ contains the independent "factors" and
$\boldsymbol{\Lambda}_{q\times d}$ is the factor loading matrix. Model fitting is carried out using the
main functionality in this package: `fastr_fit()`.

## Usage 

More to come here.
